Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-27 WSSSPE2_report/WSSSPE2_review.tex
Sections 3 and 4: Add two bib items. Modified a third bib item.

The workshop featured two keynote addresses. In the opening keynote
presentation, Kaitlin Thaney of the Mozilla Science Lab talked about her
organization's work and policy to enable and support sustainable and
reproducible scientific research through the open web. The second keynote
speaker was Neil Chue Hong of Software Sustainability Institute. He shined a
light on how scientific software is prevalently driving advances in many science
and engineering fields. Both keynote speeches spawned further discussion among
workshop participants on the crucial notion \emph{sustainability} in the theme of
our workshop.

>>>>

The workshop featured two keynote addresses. In the opening keynote
presentation~\cite{Thaney_slides}, Kaitlin Thaney of the Mozilla Science Lab talked about her
organization's work and policy to enable and support sustainable and
reproducible scientific research through the open web. The second keynote
speaker was Neil Chue Hong of Software Sustainability Institute. His talk~\cite{Hong_slides} shined a
light on how scientific software is prevalently driving advances in many science
and engineering fields. Both keynote speeches spawned further discussion among
workshop participants on the crucial notion \emph{sustainability} in the theme of
our workshop.
